Verifying Demonstrations

### 2019-07-16 paper/protest-model.tex
Cuts location proofs in related work

The strength function \(\str\) can be used to regulate the trust in the 
estimated participation count.
In general, \(\str\) can be defined as a weighted sum of the proof shares, 
\(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) being the trust in 
the witness corresponding to the proof share \(s_i\), and the threshold 
\(\theta\) represents the total trust needed to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called 
\emph{trusted witness}, participating in the protest. For instance, the role of 
the trusted witness could be taken by the independent journalist Jane.
In this situation, the weights would be 1 for trusted witnesses and 
0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a 
trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being eligible if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

>>>>

The strength function \(\str\) can be used to regulate the trust in the 
estimated participation count.
\daniel{%
  The strength function can take the size of the time interval into account 
  too, smaller time intervals around the event yields stronger proofs.
}
In general, \(\str\) can be defined as a weighted sum of the proof shares, 
\(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) being the trust in 
the witness corresponding to the proof share \(s_i\), and the threshold 
\(\theta\) represents the total trust needed to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called 
\emph{trusted witness}, participating in the protest. For instance, the role of 
the trusted witness could be taken by the independent journalist Jane.
In this situation, the weights would be 1 for trusted witnesses and 
0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a 
trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being eligible if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.
